Untitled

### 2024-08-26 code/manuscript_analysis.Rmd
better breaks

qnats1 <- seq(0, 5/6, by = 1/6)
qnats2 <- seq(1/6, 1, by = 1/6)

@@

model <- did2s(
      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.87) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))  , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

for (i in 11:19){
  df.temp <- df.spill3 %>% filter((Dist > quantile(Dist, 0.87) & Att > 0) | Att == 0 )%>% 
        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
  df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
  names(df.temp)[1:6] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
  TEs.strat.far <- rbind(TEs.strat.far, data.frame(model$coeftable)[1,])
}

model <- did2s(
      data = df.spill3  %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))  , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

>>>>

qnats1 <- seq(0, 4/5, by = 1/5)
qnats2 <- seq(1/5, 1, by = 1/5)

@@

quantile(df.spill3$Dist, 0.15, na.rm = TRUE)

model <- did2s(
      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

for (i in 11:19){
  df.temp <- df.spill3 %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 )%>% 
        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx))
  df.temp <- df.temp[,c(1:5, i, 16:ncol(df.spill3))] 
  names(df.temp)[1:6] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
  TEs.strat.far <- rbind(TEs.strat.far, data.frame(model$coeftable)[1,])
}

model <- did2s(
      data = df.spill3  %>% filter((Dist == 0 & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
